---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fpp2

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/fpp2)](https://cran.r-project.org/package=fpp2)
[![R build status](https://github.com/robjhyndman/fpp2-package/workflows/R-CMD-check/badge.svg)](https://github.com/robjhyndman/fpp2-package/actions)
[![Downloads](http://cranlogs.r-pkg.org/badges/fpp2)](https://cran.r-project.org/package=fpp2)
<!-- badges: end -->

## Overview

The R package *fpp2* loads data required for the examples and exercises used in the book [*Forecasting: Principles and Practice* (2nd edition)](https://otexts.com/fpp2) by Rob J Hyndman and George Athanasopoulos. It also loads several packages needed to do the analysis described in the book.

## Installation

You can install the **stable** version from
[CRAN](https://cran.r-project.org/package=fpp2).

```{r eval = FALSE}
install.packages('fpp2', dependencies = TRUE)
```

You can install the **development** version from
[Github](https://github.com/robjhyndman/fpp2-package)

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("robjhyndman/fpp2-package")
```

## Usage

`library(fpp2)` will load the following packages:

* [forecast](https://pkg.robjhyndman.com/forecast/), for forecasting methods and some data sets.
* [ggplot2](https://ggplot2.tidyverse.org), for data visualisation.
* [fma](https://pkg.robjhyndman.com/fma/), for data taken from the book "Forecasting: methods and applications" by Makridakis, Wheelwright and Hyndman (1998).
* [expsmooth](https://pkg.robjhyndman.com/expsmooth/), for data taken from the book "Forecasting with Exponential Smoothing" by Hyndman, Koehler, Ord and Snyder (2008).

You also get a condensed summary of conflicts with other packages you have loaded:

```{r example}
library(fpp2)
```

